\documentclass[letterpaper,10pt,titlepage, onecolumn]{IEEEtran}

\usepackage{graphicx}                                     
\usepackage{amssymb}                                       
\usepackage{amsmath}                                       
\usepackage{amsthm}  

\usepackage{alltt}                                         
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def \name{Bhavya Parikh}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {CS461 ``Senior Software Engr Project'' Problem Statement},
  pdftitle = {CS 461 Problem Statement},
  pdfsubject = {CS 461 Problem Statement},
  pdfpagemode = UseNone
}

\begin{document}

\begin{titlepage}
\begin{center}
  
  \textbf{}

  \vspace{6cm}
  \Huge{}
  \textbf{Problem Statement}
  \vspace{3cm}

 
  \LARGE
  CS461 - Senior Software Engr Project\\
  \vspace{0.25cm}
  Instructor: D. Kevin McGrath \\
  Instructor: Kristen Winters \\
  \vspace{0.25cm}
  Fall 2018 \\
  \vspace{1.5cm}
  
  \textbf{Bhavya Parikh}
  \date{October 9th, 2018}
  \vfill
  October 9th, 2018\\
  \vspace{1cm}
  \vspace*{\fill}
   \textbf{Abstract -- This paper examines what the purpose of our project is. It examines the problems involved to be faced and the tools or method we will use to come up with a solution. Lastly, this paper focuses on the performance metrics or criteria involved in this project.}
  \end{center}
  \end{titlepage}
  
\section{PROBLEM STATEMENT}

    One of the problems a lot of people in the industry face these days is to visualize their own data. The data they have gained about their employees, products or it can even be the research data that they want to visualize and show it in a presentation. In any industry, it is a must to visualize data in a good form and way. Most of the times we have a lot of data but we are not able to visualize it in a good way. Imagine I have chunks of data of students but its frustrating and annoying to use a software where just to search for one student it takes an hour. It also takes a lot of time just to go through his set of information in the database. In the similar ways in the industry employers in management needs software which can cut down the time to look up for any kind of data or information that they are looking for any particular person or an individual whether it’s an full-time employee or an part-time employee. The software should be user-friendly too.\\


    Our client from McAfee is facing a similar issue what is happening is that our client has chunks of data about IP-addresses, the hash of malware, the name of malware, geo-location of IP-address, the name of tag etc. and he is finding new ways to present data. Normally in the industry, they are often been confronted with presenting data in new or challenging ways. The presentation of data can be used on a number of occasion such as giving an presentation, writing customer-focused blogs or just blogs in general, presenting some kind of media and it can even be used in research to open up new doors to new research or finding or a new way of thinking. \\


    So our client is looking for a new way of presenting his data. At the moment he has his data saved up Microsoft Excel CSV file. He wants us to come up with ways of presenting data in a format that he can find user-friendly, has good visualization and it has to be in three dimensions. The client would prefer something similar to the Open Graffiti solution but the thing is that it is very challenging to get the data in Open Graffiti. So we have to think of a way in which the data is being taken from the CSV on a regular basis on a level that every time anyone opens the application it will be updated with data automatically on a fixed period of time. They would be able to have an visualization experience of their data such that they can easily point out stuff, it is less time consuming, user- friendly and in three dimensions. The client wants us to come up with something like that he would preferably prefer to have the data being visualized in a globe, which would be quite interesting, fun and learning experience to make. This would be a one of a kind in the industry.\\ 


     After having the first couple of meetings with the team and understanding the requirements of the project from the client's emails we have kind of figure out our approach towards the project but might still need to work on it more. We need to be more clear about the project as we at first did not know much as the project did not have any description on canvas and the client did not mention any objectives. So after contacting the client now, we are working towards our first approach. Our client is based off in the Netherlands and is nine hours ahead of us in time, which might have to manage and make it work. But it might be an issue sometimes.\\


    So the approach is going to coming up with an action plan as an team proposing an action plan to the client and see if the client likes our idea or he wants us to implement something else. We will make sure that after our every sprint our client is satisfied.We are going to be using an agile method and make sprints for this project. We will try to have our best teamwork happen using good communication, time management and meet all the deadlines on time. This way we will try our utmost best to make the project happen for our client and make it so that it is to our and our client’s satisfaction. Lastly we would like to build some ting which can may be something which even can used by others and can even help them out. \\

 
   


\end{document}